---
title: "R Notebook"
output: html_notebook
---

Loading requierd libraries
```{r}
(library(ggplot2))
(library(tidyr))
(library(dplyr))
(library(readxl))
(library(gridExtra))
(library(plotly))
```

Getting the complete raw data
```{r}
raw.data <- read.csv("data/Fifa19C.csv",stringsAsFactors = F)
```


Selecting only the required columns from the complete dataframe
```{r}
data <- raw.data %>% select(ID,Name,Age,Nationality,Overall,Potential,Club,Value,Wage,Preferred.Foot,International.Reputation,Weak.Foot,Skill.Moves,Position,Jersey.Number,Height,Weight,Release.Clause)
```


Converting categorical values to factors
```{r}
data$International.Reputation <- as.factor(data$International.Reputation)
data$Weak.Foot <- as.factor(data$Weak.Foot)
data$Skill.Moves <- as.factor(data$Skill.Moves)
data$Jersey.Number <- as.factor(data$Jersey.Number)


head(data)
```


```{r}
toNumberCurrency <- function(vector) {
    vector <- as.character(vector)
    #replace '???' with 'Euro sign'
    vector <- gsub("(???|,)","", vector) 
    result <- as.numeric(vector)
   
    k_positions <- grep("K", vector)
    result[k_positions] <- as.numeric(gsub("K","",vector[k_positions])) * 1000
  
    m_positions <- grep("M", vector)
    result[m_positions] <- as.numeric(gsub("M","",vector[m_positions])) * 1000000
    
    return(result)
}
data$Wage <- toNumberCurrency(data$Wage) 
data$Value <- toNumberCurrency(data$Value)
data$Release.Clause <- toNumberCurrency(data$Release.Clause)
```

```{r}
head(data)
```


Converting height to centimeters
```{r}
l <- strsplit(data$Height,"'",fixed = T)
data$Height <- sapply(l, function(x) sum(as.numeric(x)*c(30.4,2.54)))
```

Removing lbs from the weight column
```{r}
data$Weight <- gsub("[a-zA-Z ]", "", data$Weight)
data$Weight <- as.numeric(data$Weight)
```

Replace specefic positions of players with more general positions
```{r}
data$Position <- if_else(data$Position=="ST" | data$Position=="RS" | data$Position=="LS","ST",data$Position)
data$Position <- if_else(data$Position=="LF" | data$Position=="LW","LW",data$Position)
data$Position <- if_else(data$Position=="RF" | data$Position=="RW","RW",data$Position)
data$Position <- if_else(data$Position=="CM" | data$Position=="RCM" | data$Position=="LCM","CM",data$Position)
data$Position <- if_else(data$Position=="CB" | data$Position=="RCB" | data$Position=="LCB","CB",data$Position)
data$Position <- if_else(data$Position=="CDM" | data$Position=="LDM" | data$Position=="RDM","CDM",data$Position)
data$Position <- if_else(data$Position=="CAM" | data$Position=="LAM" | data$Position=="RAM","CAM",data$Position)
head(data)
```

Total players based on position
```{r}
pl <- ggplot(data,aes(x = Position)) + geom_bar() + theme_minimal() 
ggplotly(pl)
```

Getting top players using order
```{r}
top.players <- data[order(data$Overall,decreasing = T),]
```

```{r}
top.25 <- head(top.players,25)
```

Jersey numbers for the top 25 players
```{r}
pl <- ggplot(top.25,aes(Jersey.Number)) + geom_bar() + theme_minimal() 
ggplotly(pl)
```

Ages of top 25 players
```{r}
pl <- ggplot(top.25,aes(Age)) + geom_histogram(binwidth = 1) + theme_minimal() 
ggplotly(pl)
```

Top 25 based on countries
```{r}
pl <- ggplot(top.25,aes(Nationality)) + geom_bar() + theme_minimal() + theme(axis.text.x = element_text(angle = 45,hjust = 1))
ggplotly(pl)
```

Top 25 by position
```{r}
pl <- ggplot(top.25,aes(x = Position,fill = Name)) + geom_bar() + theme_minimal() 
ggplotly(pl)
```

Getting the top potential players with age < 25 
```{r}
top.potential <- data %>% filter(Age<=25) %>% arrange(desc(Potential))
head(top.potential)
```

```{r}
top.50.potential <- head(top.potential,50)
```

Clubs of top 50 potential players
```{r}
pl <- ggplot(top.50.potential,aes(x=Nationality)) + geom_bar(aes(fill=Name)) + theme_minimal() + theme(axis.text.x = element_text(angle = 45,hjust = 1))
ggplotly(pl)
```


```{r}
temp <- top.50.potential[order(top.50.potential$Age,top.50.potential$Value,-top.50.potential$Potential,-top.50.potential$Overall),]
head(temp)
```

```{r}
top.25.and.top.50.potential <- rbind(top.25,top.50.potential)
```

Top 50 players based on Club
```{r}
pl <- ggplot(top.50.potential,aes(x=Club)) + geom_bar() + theme_minimal() + theme(axis.text.x = element_text(angle = 45,hjust = 1))
ggplotly(pl)
```





